---
title: "Project_Final"
author: "Joo Kim"
date: '2022-05-19'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(lubridate)
library(tidyr)
library(gridExtra)
library(reshape2)
library(tseries)
library(DescTools)
library("TTR")
library(Kendall)
library(patchwork)
library(ggpubr)
library(corrplot)
library(tidyverse)
```


# Data Dictionary

| Field Name | Data Type | Description                                                    | Example             |
|:------------:|:-----------:|:----------------------------------------------------------------|:---------------------|
| Date_UTC   | character | Date (Universal Time Correlated)                               | 2000-01-01T00:00:00 |
| dbn_nez    | float     | Magnetic field north component, NEZ coordinates [nT]           | -51.6               |
| dbe_nez    | float     | Magnetic field east component, NEZ coordinates [nT]            | -5.7                |
| dbz_nez    | float     | Magnetic field vertical component, NEZ coordinates [nT]        | 15.0                |
| dbn_geo    | float     | Magnetic field north component, geographic coordinates [nT]    | -51.8               |
| dbe_geo    | float     | Magnetic field east component, geographic coordinates [nT]     | 3.5                 |
| dbz_geo    | float     | Magnetic field vertical component, geographic coordinates [nT] | 15.0                |
| Extent     | double    | Extent of Record [seconds]                                     | 60                  |
| IAGA       | character | Station Identifier                                             | FRD                 |
| GEOLON     | float     | Geographic Longitude [degrees]                                 | 282.63              |
| GEOLAT     | float     | Geographic Latitude [degrees]                                  | 38.2                |
| MAGON      | float     | AACGM Longitude [degrees]                                      | -2.13               |
| MAGLAT     | float     | AACGM Latitude [degrees]                                       | 49.08               |
| MLT        | float     | AACGM Magnetic Local Time [h]                                  | 18.70               |
| MCOLAT     | float     | AACGM Colatitude [degrees]                                     | 40.92               |
| IGRF_DECL  | float     | Magnetic Declination [degrees]                                 | -10.18              |
| SZA        | float     | Solar Zenith Angle [degrees]                                   | 113.02              |

- NEZ: North, East, Vertical directions
- AACGM: Altitude adjusted corrected geomagnetic
- nT: nano tesla (a unit of magnetic flux)


# Visualizations

## Daily Data

```{r}
df = read.table("FRD2001.csv", sep = ',', header = T)
df_sample = df[(1:nrow(df) - 1) %% 24 == 0 ,]
df_sample$Date = ymd(substr(df_sample$Date_UTC, 1, 10))

df_sample = gather(df_sample, "Variables", "value",  c(2:7))
```

```{r}
p <- ggplot(aes(x = Date, y = value, colour = Variables), data = df_sample) +
  geom_line() + facet_grid(rows = vars(Variables), scales = "free") +
  scale_x_date(date_labels = "%b") +
  ggtitle("FRD 2001 Daily Data") +
  theme_bw() +
  theme(plot.title = element_text(face="bold", size=15), text = element_text(size = 12),
        legend.background = element_rect(fill = "white", size = 6, colour = "white"),
        strip.text.y = element_blank(),
        legend.text=element_text(size=12)) +
  scale_color_brewer(name="Variables",
                     labels=c("east_geo","east_nez","north_geo","north_nez","vertical_geo","vertical_nez"),
                     palette="Paired")

p
```
## Correlation matrix

```{r}
clk <- read.csv("clk2001_samples.csv")
frd <- read.csv("FRD2001.csv")
```

```{r}
# keep only relevant variables
clk <- clk[,c("Date_UTC","dbn_nez","dbn_geo","dbe_nez","dbe_geo","dbz_nez","dbz_geo")]
frd <- frd[,c("Date_UTC","dbn_nez","dbn_geo","dbe_nez","dbe_geo","dbz_nez","dbz_geo")]
```

```{r}
# number of rows of the data
print(nrow(clk))
print(nrow(frd))
```

```{r}
# hourly data
clk2 = clk[(1:nrow(clk)-1) %% 60 == 0 ,]
frd2 = frd
```

```{r}
# check the n of rows
print(nrow(clk2))
print(nrow(frd2))
```



```{r}
# getting correlation matrix
clk_cor = cor(clk2[,2:7], use = "complete.obs", method = c("kendall"))
frd_cor = cor(frd2[,2:7], use = "complete.obs", method = "kendall")
```

```{r}
corrplot(clk_cor, type = "upper", order = "original",
         tl.col = "black", tl.srt = 45, title = "Correlation Plot of CLK Station",
         mar=c(0,0,2,0))
```

```{r}
corrplot(frd_cor, type = "upper", order = "original", 
         tl.col = "black", tl.srt = 45, title = "Correlation Plot of FRD Station",
         mar=c(0,0,2,0))
```

## Density plots
```{r}
frd2001 <- read.table("frd2001_samples.csv", sep = ',', header = T)
mfrd2001 <- melt(frd2001[,c("Date_UTC","dbn_nez","dbe_nez","dbz_nez")], id = "Date_UTC")
mfrd2001_g <- melt(frd2001[,c("Date_UTC","dbn_geo","dbe_geo","dbz_geo")], id = "Date_UTC")
```


```{r}
# NEZ coordinates
ggplot(mfrd2001, aes(x=value, color=variable, fill=variable)) + 
  geom_density(alpha=0.05) +
  facet_grid(rows = vars(variable)) +
  ggtitle("Density Plot for Magnetic Field (NEZ coordinates) [FRD 2001]") +
  xlab("Magnetic Field (nT)") +
  ylab("Density") +
  theme_classic()
```
```{r}
# geo coordinates
ggplot(mfrd2001_g, aes(x=value, color=variable, fill=variable)) + 
  geom_density(alpha=0.05) +
  facet_grid(rows = vars(variable)) +
  ggtitle("Density Plot for Magnetic Field (geographic coordinates) [FRD 2001]") +
  xlab("Magnetic Field (nT)") +
  ylab("Density") +
  theme_classic()
```



## acf of hourly and daily data

```{r}
frd2001 <- read.table("frd2001_samples.csv", sep = ',', header = T)
nrow(frd2001)
```


```{r}
# finding the max magnitude value
max_abs = function(x){
  x = na.omit(x)
  if(length(x) == 0) return (0)
  else{
    return(x[which.max(abs(x))])  
  }
}

# obtaining daily data (using max_abs)
daily_pooling = function(df, varname, func)
{
  y = as.vector(df[, varname])
  y = matrix(y, ncol = 24, byrow = T)
  y = apply(y, 1, func) # max pooling
  return(y)
}
```


```{r}
# summarizing into daily data
daily_dbn <- daily_pooling(frd2001, "dbn_nez", max_abs)
daily_dbe <- daily_pooling(frd2001, "dbe_nez", max_abs)
daily_dbz <- daily_pooling(frd2001, "dbz_nez", max_abs)
```

```{r}
par(mar=c(3,3,3,0))
acf_dbn_h <- acf(frd2001$dbn_nez[!is.na(frd2001$dbn_nez)], plot = FALSE)
plot(acf_dbn_h[1:20], main="Autocorrelation for Hourly Data (north_nez)", ylim=c(-0.1,0.9))
```
```{r}
par(mar=c(3,3,3,0))
acf_dbn_d <- acf(daily_dbn, plot = FALSE)
plot(acf_dbn_d[1:20], main = "Autocorrelation for Daily Data (north_nez)", ylim=c(-0.1,0.9))
```

```{r}
par(mar=c(3,3,3,0))
acf_dbe_h <- acf(frd2001$dbe_nez[!is.na(frd2001$dbe_nez)], plot = FALSE)
plot(acf_dbe_h[1:20], main="Autocorrelation for Hourly Data (east_nez)", ylim=c(-0.1,0.9))
```

```{r}
par(mar=c(3,3,3,0))
acf_dbe_d <- acf(daily_dbe, plot = FALSE)
plot(acf_dbe_d[1:20], main = "Autocorrelation for Daily Data (east_nez)", ylim=c(-0.1,0.9))
```

```{r}
par(mar=c(3,3,3,0))
acf_dbz_h <- acf(frd2001$dbz_nez[!is.na(frd2001$dbz_nez)], plot = FALSE)
plot(acf_dbz_h[1:20], main="Autocorrelation for Hourly Data (east_nez)", ylim=c(-0.1,0.9))
```


```{r}
par(mar=c(3,3,3,0))
acf_dbz_d <- acf(daily_dbz, plot = FALSE)
plot(acf_dbz_d[1:20], main = "Autocorrelation for Daily Data (vertical_nez)", ylim=c(-0.1,0.9))
```
## Comparing Stations

```{r}
clk <- read.csv("CLK2001_2.csv")
msh <- read.csv("MSH2001.csv")

clk <- clk[,c("Date_UTC","dbn_nez","dbn_geo","dbe_nez","dbe_geo","dbz_nez","dbz_geo")]
frd <- frd[,c("Date_UTC","dbn_nez","dbn_geo","dbe_nez","dbe_geo","dbz_nez","dbz_geo")]
msh <- msh[,c("Date_UTC","dbn_nez","dbn_geo","dbe_nez","dbe_geo","dbz_nez","dbz_geo")]

clk2 = clk[(1:nrow(clk)-1) %% 60 == 0 ,]
frd2 = frd
msh2 = msh[(1:nrow(clk)-1) %% 60 == 0 ,]

# check the number of rows for each data is consistent
print(nrow(clk2))
print(nrow(frd2))
print(nrow(msh2))
```

```{r}
# Date
clk2$Date = ymd(substr(clk2$Date_UTC, 1, 10))
frd2$Date = ymd(substr(frd2$Date_UTC, 1, 10))
msh2$Date = ymd(substr(msh2$Date_UTC, 1, 10))
```


```{r}
# For the presentation
p1 <- ggplot() +
  geom_line(data = clk2, aes(x = Date, y = dbn_nez), color = "red") +
  scale_x_date(date_labels = "%b") +
  ggtitle("CLK 2001 Hourly Data (North)") +
  theme_bw() +
  ylim(-1100, 300) +
  xlab("") + ylab("")
p2 <- ggplot() +
  geom_line(data = frd2, aes(x = Date, y = dbn_nez), color = "orange") +
  scale_x_date(date_labels = "%b") +
  ggtitle("FRD 2001 Hourly Data (North)") +
  theme_bw() +
  ylim(-1100, 300) +
  xlab("") + ylab("")
p3 <- ggplot() +
  geom_line(data = msh2, aes(x = Date, y = dbn_nez), color = "darkblue") +
  scale_x_date(date_labels = "%b") +
  ggtitle("MSH 2001 Hourly Data (North)") +
  theme_bw() +
  ylim(-1100, 300) +
  ylab("")

p1 / p2 / p3
```

```{r}
p1 <- ggplot() +
  geom_line(data = clk2, aes(x = Date, y = dbe_nez), color = "red") +
  scale_x_date(date_labels = "%b") +
  ggtitle("CLK 2001 Hourly Data (East)") +
  theme_bw() +
  ylim(-500, 400) +
  xlab("") + ylab("dbe_nez (nT)")
p2 <- ggplot() +
  geom_line(data = frd2, aes(x = Date, y = dbe_nez), color = "orange") +
  scale_x_date(date_labels = "%b") +
  ggtitle("FRD 2001 Hourly Data (East)") +
  theme_bw() +
  ylim(-500, 400) +
  xlab("") + ylab("dbe_nez (nT)")
p3 <- ggplot() +
  geom_line(data = msh2, aes(x = Date, y = dbe_nez), color = "darkblue") +
  scale_x_date(date_labels = "%b") +
  ggtitle("MSH 2001 Hourly Data (East)") +
  theme_bw() +
  ylim(-500, 400) +
  ylab("dbe_nez (nT)")

p1 / p2 / p3
```

```{r}
p1 <- ggplot() +
  geom_line(data = clk2, aes(x = Date, y = dbz_nez), color = "red") +
  scale_x_date(date_labels = "%b") +
  ggtitle("CLK 2001 Hourly Data (Vertical)") +
  theme_bw() +
  ylim(-450, 300) +
  xlab("") + ylab("dbz_nez (nT)")
p2 <- ggplot() +
  geom_line(data = frd2, aes(x = Date, y = dbz_nez), color = "orange") +
  scale_x_date(date_labels = "%b") +
  ggtitle("FRD 2001 Hourly Data (Vertical)") +
  theme_bw() +
  ylim(-450, 300) +
  xlab("") + ylab("dbz_nez (nT)")
p3 <- ggplot() +
  geom_line(data = msh2, aes(x = Date, y = dbz_nez), color = "darkblue") +
  scale_x_date(date_labels = "%b") +
  ggtitle("MSH 2001 Hourly Data (Vertical)") +
  theme_bw() +
  ylim(-450, 300) +
  ylab("dbz_nez (nT)")

p1 / p2 / p3
```

## Correlation of same variables from different stations

```{r}
# for presentation
par(mar=c(3,3,3,0))
ggplot(data = data.frame(x = clk2$dbn_nez, y = frd2$dbn_nez), aes(x=x, y=y)) +
  geom_point() +
  stat_cor(method = "pearson", label.x = -1000, label.y = 150, size=7) +
  theme_bw() +
  ggtitle("The Correlation between north_nez Variables from Different Stations (CLK, FRD)") +
  xlab("CLK") +
  ylab("FRD") +
  theme(plot.title = element_text(face="bold", size=12))
```
```{r}
ggplot(data = data.frame(x = clk2$dbe_nez, y = frd2$dbe_nez), aes(x=x, y=y)) +
  geom_point() +
  stat_cor(method = "pearson", label.x = -900, label.y = 100) +
  theme_bw() +
  ggtitle("The Correlation between dbe_nez Variables from Different Stations (CLK, FRD)") +
  xlab("dbe_nez from CLK") +
  ylab("dbe_nez from FRD")
```


```{r}
ggplot(data = data.frame(x = clk2$dbz_nez, y = frd2$dbz_nez), aes(x=x, y=y)) +
  geom_point() +
  stat_cor(method = "pearson", label.x = -900, label.y = 150) +
  theme_bw() +
  ggtitle("The Correlation between dbz_nez Variables from Different Stations (CLK, FRD)") +
  xlab("dbz_nez from CLK") +
  ylab("dbz_nez from FRD")
```







